### 2014-10-24 PrivacyProtection-2014-09-09.tex
Added short description of Implementation.
finsihed spec of excessive data mining

%1. Excessive Data Mining
%------------------------
%Description: The Service Provider and/or the Local Authority extract more private information from the collected data, than the citizen agreed to.
%E.g. the Service Provider wants to test a new product, and uses old data collected for a different purpose.
%E.g. the Local Authority wants to analyze collected data from fare evasions.
%
%COI: Privacy vs. Buisness Intelligence of Local Authority, Privacy vs. Financial Profit of Serivce Provider.
%Vuln.: Lax data handling policies; Unaware citizen; Weak law enforcement
%Affected Data: Potential Information extracted from raw data.
%
%Likeliness: High
%Loss:      Medium (Control is lost, no direct harm done)
%Risk:      5
%
\textbf{Excessive Data Mining}
Lorem Ipsum

>>>>

%1. Excessive Data Mining
%------------------------
%Description: The Service Provider and/or the Local Authority extract more private information from the collected data, than the citizen agreed to.
%E.g. the Service Provider wants to test a new product, and uses old data collected for a different purpose.
%E.g. the Local Authority wants to analyze collected data from fare evasions.
%
%COI: Privacy vs. Buisness Intelligence of Local Authority, Privacy vs. Financial Profit of Serivce Provider.
%Vuln.: Lax data handling policies; Unaware citizen; Weak law enforcement
%Affected Data: Potential Information extracted from raw data.
%
%Likeliness: High
%Loss:      Medium (Control is lost, no direct harm done)
%Risk:      5
%
\textbf{Excessive Data Mining.}
The System Provider and/or the Local Authority secretly extract more private information from the collected data, than the Citizen agreed to.
But results of the mining process create no disadvantages for Citizens, because there is no disclosure to third parties.
This could be the case for a System Provider, who wants to test a new product and uses the pre-existing data collection.
Or for a Local Authority, who wants to analyze the data collection regarding fare evasion.
However, the Citizen has not agreed to such data processing nor could he, since it is conducted secretly.
This disables a Citizen to control his data adequately.
Thus there are two possible conflicts: \textit{Privacy vs. Financial Profit of Serivce Provider} and  \textit{Privacy vs. Buisness Intelligence of Local Authority}
The threat can be provoked by either lax data handling policies of both System Providers and Local Authorities, or a weak law enforcement of existing supervision.
But the main issue, which can lead to such threats, is again a general \textit{Missing Privacy Awareness}.
